Dynamic Bandwidth Allocation with Minimum Rate Guarantees Using OpenFlow

### 2019-04-11 giformat/draft.tex
Added results numbers to paper

@@

\newauthor{mm}{Joel van Egmond}{}
% Can add more authors
%\newauthor{se}{Someone Else}{}
%\newauthor{ya}{Yet Another}{}
%\newauthor{fa}{Fourth Author}{}

@@

Where $M_{max}$ is a meter maximum rate, and $R$ is the link transmission rate. This is to say the minimum rates will always be guaranteed so long as the sum of the minimum rates is not greater than the maximum link rate. This solution requires a minimum of only two queues for n clients, addressing the initial design's scalability issue.

@@

@@

@@

>>>>

\usepackage{caption}
\captionsetup[table]{skip=0pt}
\captionsetup[table]{font=small}

@@

\newauthor{mm}{Joel van Egmond}{}
% Can add more authors
\newauthor{se}{Maryam Elahi}{}
\newauthor{ya}{Mea Wang}{}
%\newauthor{fa}{Fourth Author}{}

@@

where $M_{max}$ is a meter maximum rate, and $R$ is the link transmission rate. This is to say the minimum rates will always be guaranteed so long as the sum of the minimum rates is not greater than the maximum link rate. This solution requires a minimum of only two queues for n clients, addressing the initial design's scalability issue.

@@

EXPLAIN FIX TO THIS

@@

\subsection{Test Setups}
\label{result_setups}

testbed diagrams/explanation for why theres a loop

\subsection{Tests}
\label{result_tests}

describe the conflict and non conflict tests, that they are run on every setup
describe the over time test for dba

\subsection{No Guarantee}
\label{no_guar}

Intro of tests.

non compete

\begin{table}[h]
	\label{ng_nc}
	\vspace{-3mm}
	\begin{center}
		\begin{small}
			\begin{tabular}{cccc}
				%\hline
				Protocol & Host & Demand & Actual \\
				\hline
				UDP & Host 1 & 200 & 210\\
				    & Host 2 & 300 & 315\\
				\hline
				TCP & Host 1 & 200 & 210\\
				    & Host 2 & 300 & 315\\
			\end{tabular}
		\end{small}
	\end{center}
	\caption{Bandwidth usage for non-competing hosts in no guarantee setup.\\
	Host 1 minimum rate guarantee: 100 Mbps\\
	Host 2 minimum rate guarantee: 200 Mbps\\	
	Total available bandwidth: 600 Mbps}
	\vspace{-3mm}
\end{table}

short analysis

compete

\begin{table}[h]
	\label{ng_c}
	\vspace{-3mm}
	\begin{center}
		\begin{small}
			\begin{tabular}{cccc}
				%\hline
				Protocol & Host & Demand & Actual \\
				\hline
				UDP & Host 1 & 400 & 301\\
				    & Host 2 & 400 & 301\\
				\hline
				TCP & Host 1 & 400 & 315\\
				    & Host 2 & 400 & 277\\
			\end{tabular}
		\end{small}
	\end{center}
	\caption{Bandwidth usage for competing hosts in no guarantee setup.\\
	Host 1 minimum rate guarantee: 100 Mbps\\
	Host 2 minimum rate guarantee: 200 Mbps\\	
	Total available bandwidth: 600 Mbps}
	\vspace{-3mm}
\end{table}

short analysis

\subsection{Minimum Rate Guarantee}
\label{min_guar}

Intro of tests.

non compete

\begin{table}[h]
	\label{mg_nc}
	\vspace{-3mm}
	\begin{center}
		\begin{small}
		\setlength\tabcolsep{1.5pt}
			\begin{tabular}{cccccc}
				%\hline
				Protocol & Host & Demand & Actual & High Prio & Remarked \\
				\hline
				UDP & Host 1 & 200 & 210 & 96 & 111\\
				    & Host 2 & 300 & 315 & 192 & 119\\
				\hline
				TCP & Host 1 & 200 & 210 & 96 & 115\\
				    & Host 2 & 300 & 315 & 192 & 125\\
			\end{tabular}
		\end{small}
	\end{center}
	\caption{Bandwidth usage for non-competing hosts in minimum guarantee setup.\\
	Host 1 minimum rate guarantee: 100 Mbps\\
	Host 2 minimum rate guarantee: 200 Mbps\\	
	Total available bandwidth: 600 Mbps}
	\vspace{-3mm}
\end{table}

short analysis

compete

\begin{table}[h]
	\label{mg_c}
	\vspace{-3mm}
	\begin{center}
		\begin{small}
		\setlength\tabcolsep{1.5pt}
			\begin{tabular}{cccccc}
				%\hline
				Protocol & Host & Demand & Actual & High Prio & Remarked \\
				\hline
				UDP & Host 1 & 400 & 322 & 96 & 319\\
				    & Host 2 & 400 & 322 & 192 & 223\\
				\hline
				TCP & Host 1 & 400 & 233 & 96 & 103\\
				    & Host 2 & 400 & 359 & 191 & 145\\
			\end{tabular}
		\end{small}
	\end{center}
	\caption{Bandwidth usage for competing hosts in minimum guarantee setup.\\
	Host 1 minimum rate guarantee: 100 Mbps\\
	Host 2 minimum rate guarantee: 200 Mbps\\	
	Total available bandwidth: 600 Mbps}
	\vspace{-3mm}
\end{table}

short analysis

\subsection{Egalitarian Fairness}
\label{dba_egal}

Intro of tests.

non compete

\begin{table}[h]
	\label{egal_nc}
	\vspace{-3mm}
	\begin{center}
		\begin{small}
		\setlength\tabcolsep{1.5pt}
			\begin{tabular}{cccccccc}
				%\hline
				Protocol & Host & Demand & Expected & Actual & High & Mid & Low\\
				\hline
				UDP & Host 1 & 200 & 200 & 199 & 98 & 109 & 4\\
				    & Host 2 & 300 & 300 & 307 & 199 & 117 & 3\\
				\hline
				TCP & Host 1 & 200 & 200 & 75 & 63 & 5 & 13\\
				    & Host 2 & 300 & 300 & 315 & 199 & 127 & 1\\
			\end{tabular}
		\end{small}
	\end{center}
	\caption{Bandwidth usage for non-competing hosts in egalitarian fairness setup.\\
	Host 1 minimum rate guarantee: 100 Mbps\\
	Host 2 minimum rate guarantee: 200 Mbps\\	
	Total available bandwidth: 600 Mbps}
	\vspace{-3mm}
\end{table}

short analysis

compete

\begin{table}[h]
	\label{egal_c}
	\vspace{-3mm}
	\begin{center}
		\begin{small}
		\setlength\tabcolsep{1.5pt}
			\begin{tabular}{cccccccc}
				%\hline
				Protocol & Host & Demand & Expected & Actual & High & Mid & Low\\
				\hline
				UDP & Host 1 & 400 & 250 & 242 & 98 & 178 & 175\\
				    & Host 2 & 400 & 350 & 370 & 197 & 175 & 38\\
				\hline
				TCP & Host 1 & 400 & 250 & 85 & 73 & 6 & 14\\
				    & Host 2 & 400 & 350 & 419 & 197 & 234 & 3\\
			\end{tabular}
		\end{small}
	\end{center}
	\caption{Bandwidth usage for competing hosts in egalitarian fairness setup.\\
	Host 1 minimum rate guarantee: 100 Mbps\\
	Host 2 minimum rate guarantee: 200 Mbps\\	
	Total available bandwidth: 600 Mbps}
	\vspace{-3mm}
\end{table}

short analysis

Over time graphs

short analysis

\subsection{Proportional Fairness}
\label{dba_prop}
Intro of tests.

non compete

\begin{table}[h]
	\label{prop_nc}
	\vspace{-3mm}
	\begin{center}
		\begin{small}
		\setlength\tabcolsep{1.5pt}
			\begin{tabular}{cccccccc}
				%\hline
				Protocol & Host & Demand & Expected & Actual & High & Mid & Low\\
				\hline
				UDP & Host 1 & 200 & 200 & 199 & 98 & 109 & 4\\
				    & Host 2 & 300 & 300 & 308 & 198 & 118 & 2\\
				\hline
				TCP & Host 1 & 200 & 200 & 86 & 78 & 5 & 15\\
				    & Host 2 & 300 & 300 & 314 & 197 & 96 & 19\\
			\end{tabular}
		\end{small}
	\end{center}
	\caption{Bandwidth usage for non-competing hosts in proportional fairness setup.\\
	Host 1 minimum rate guarantee: 100 Mbps\\
	Host 2 minimum rate guarantee: 200 Mbps\\	
	Total available bandwidth: 600 Mbps}
	\vspace{-3mm}
\end{table}

short analysis

compete

\begin{table}[h]
	\label{prop_c}
	\vspace{-3mm}
	\begin{center}
		\begin{small}
		\setlength\tabcolsep{1.5pt}
			\begin{tabular}{cccccccc}
				%\hline
				Protocol & Host & Demand & Expected & Actual & High & Mid & Low\\
				\hline
				UDP & Host 1 & 400 & 200 & 198 & 98 & 102 & 223\\
				    & Host 2 & 400 & 400 & 397 & 197 & 207 & 13\\
				\hline
				TCP & Host 1 & 400 & 200 & 91 & 73 & 6 & 14\\
				    & Host 2 & 400 & 400 & 419 & 197 & 235 & 2\\
			\end{tabular}
		\end{small}
	\end{center}
	\caption{Bandwidth usage for competing hosts in proportional fairness setup.\\
	Host 1 minimum rate guarantee: 100 Mbps\\
	Host 2 minimum rate guarantee: 200 Mbps\\	
	Total available bandwidth: 600 Mbps}
	\vspace{-3mm}
\end{table}

short analysis

Over time graphs

short analysis

\subsection{Hybrid Proportional Fairness}
\label{dba_hybr}
Intro of tests.

non compete

\begin{table}[h]
	\label{hybr_nc}
	\vspace{-3mm}
	\begin{center}
		\begin{small}
		\setlength\tabcolsep{1.5pt}
			\begin{tabular}{cccccccc}
				%\hline
				Protocol & Host & Demand & Expected & Actual & High & Mid & Low\\
				\hline
				UDP & Host 1 & 200 & 200 & 201 & 98 & 110 & 3\\
				    & Host 2 & 300 & 300 & 309 & 199 & 120 & 1\\
				\hline
				TCP & Host 1 & 200 & 200 & 103 & 75 & 15 & 17\\
				    & Host 2 & 300 & 300 & 315 & 197 & 128 & 0\\
			\end{tabular}
		\end{small}
	\end{center}
	\caption{Bandwidth usage for non-competing hosts in hybrid proportional fairness setup.\\
	1/10th of minimum prioritized\\	
	Host 1 minimum rate guarantee: 100 Mbps\\
	Host 2 minimum rate guarantee: 200 Mbps\\	
	Total available bandwidth: 600 Mbps}
	\vspace{-3mm}
\end{table}

short analysis

compete

\begin{table}[h]
	\label{hybr_c}
	\vspace{-3mm}
	\begin{center}
		\begin{small}
		\setlength\tabcolsep{1.5pt}
			\begin{tabular}{cccccccc}
				%\hline
				Protocol & Host & Demand & Expected & Actual & High & Mid & Low\\
				\hline
				UDP & Host 1 & 400 & 245 & 238 & 98 & 149 & 180\\
				    & Host 2 & 400 & 355 & 369 & 197 & 170 & 37\\
				\hline
				TCP & Host 1 & 400 & 245 & 80 & 67 & 5 & 13\\
				    & Host 2 & 400 & 355 & 419 & 198 & 236 & 4\\
			\end{tabular}
		\end{small}
	\end{center}
	\caption{Bandwidth usage for competing hosts in hybrid proportional fairness setup.\\
	1/10th of minimum prioritized\\
	Host 1 minimum rate guarantee: 100 Mbps\\
	Host 2 minimum rate guarantee: 200 Mbps\\	
	Total available bandwidth: 600 Mbps}
	\vspace{-3mm}
\end{table}

short analysis

Over time graphs

short analysis

\subsection{Overall Result Analysis}
\label{result_analysis}

UDP good
TCP bad

@@

Overall, is the approach we took promising?
What different approach or variant of this approach is better?
What follow-up work should be done next?
What did we learn by doing this project?
